### 2018-06-29 README.Rmd
some function documentation

Before we can use most `taxald` functions, we need to do a one-time installation of the database `taxald` uses for almost all commands.  This can take a while to run, but needs only be done once.  The database is installed on your local harddisk and will persist between R sessions.  Download and install the database

@@

```

@@

>>>>

Before we can use most `taxald` functions, we need to do a one-time installation of the database `taxald` uses for almost all commands.  This can take a while to run, but needs only be done once.  The database is installed on your local harddisk and will persist between R sessions.  Download and install the database like so:

@@

create_taxadb()
```

By default, this will install the database into a hidden `.taxald` folder in your home directory (`~/.taxald`).  You can control this by passing the path to `create_taxadb()` or setting the environmental variable `TAXALD_HOME` to a different location.

This function downloads each of the individual tables and loads them into a [MonetDBLite](https://www.monetdb.org) database.  (MonetDBLite is much like SQLite, requiring no external server setup.  However, for our purposes, MonetDB's columnar design provides significantly faster performance than SQLite, Postgres, or even some in-memory operations in `dplyr`.)

Currently tables are pulled from the development cache on GitHub. Many of these tables are still being cleaned up and standardized, see [schema.md](schema.md).  Multiple tablesare provided for each authority, though some of these contain redundant information, different orientations may prove more convenient or computationally efficient.

@@

Once the database is installed, we can start to make some queries.

First, let's get a nice big species list, say, all the birds (known to the Catalogue of Life):

```{r}
df <- descendents(name = "Aves", rank = "class", authority="col")
```
